### 2021-12-07 paper/main.tex
analysis&paper

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{float}
\usepackage{booktabs,dcolumn}
\usepackage{indentfirst}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{lscape}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\newcolumntype{d}{D{.}{.}{2.5}}           % alignment on decimal marker
\newcommand\mc[1]{\multicolumn{1}{c}{#1}}
\usepackage{url} % not crucial - just used below for the URL

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-1in}%
\addtolength{\evensidemargin}{-1in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

\begin{document}

%\bibliographystyle{natbib}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if0\blind
{
  \title{\bf Turkish Elections and Catastrophic Events}
    {
}

  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Title}
\end{center}
  \medskip
} \fi

\spacingset{1.45} % DON'T change the spacing!
\section{Introduction}
\label{sec:intro}

A year ago, Turkey celebrated it's first century of being a democracy and only in 2 years, celebrations for being a republic is on the line. Yet, the country, which resides possibly one of the lesser stable regions in the world; suffered a lot during this period, while trying to establish their democratic traditions. Having survived 3 coups,

The stages for our analysis are as follows. 
First, we identify that there are more cases closed at the end of the month, which can be considered as an expeditious decision. (See \ref{fig:figure1} and \ref{fig:figure2} in appendix), in any given month, for any court type and case type. Then we show, that cases closed at the end of the month are more likely to be appealed than cases closed at any other period. (See \ref{fig:figure3} in appendix) Subsequently, we examine the performance of firms with different party roles (Respondent and Plaintiff) that are involved with a case in our data using several performance indicators such as firm profit, firm current assets and number of employees in a 6 year time window, 3 years before the closure of the case and 3 years after the closure of the case.

We are hoping to stress the importance of a judicial systems on well being and growth of the county by drawing parallels with the judicial structures and firm performance that derive growth. This paper will be the first to evaluate the adverse effects on performance of firms involved in a lawsuit by the quality of the judicial decision. The quality of the decision is, in theory, highly affected by the deadlines set by the government.

\section{Literature Review}

Previous research also show the impact of deadline quotas on judge behavior. de Figueiredo et al. evaluates the effects of a requirement of federal district court judges to publicly release their backlog on their behaviour. They report that such a quota incentives judges to close considerably more cases right before the deadline week\href{ref:ref1}{(de Figueiredo et al., 2017)}. Similar deadline effects are also present in different fields. (Lewis & Bajari, 2014), (Asch, 1990), (Oyer, 1998), (Frakes & Wasserman, 2016) and (Liebman & Mahoney, 2017) discuss the "bunching" of work completion right before the deadline in construction, military recruitment, sales, patent examination and end of the year spending by government agencies respectively. Cohen et.al investigates deadlines medical drug approval deadlines. Echoed in our research's outline, they first reveal that there is a global surge in drug approvals right before the approval deadlines. Consequently, they argue that these swift decisions are associated with more adverse effects such as death, hospitalization etc. (Cohen et al., 2019). Carpenter and Grimmer discuss the downside of government imposed decision making deadlines and derive a model that demonstrates the increase error rate in decision making.(Daniel & Grimmer., 2009). While our research is comparable with de Figueiredo et al. in terms of how deadline quotas effect judge behaviour on case closure and Cohen et al. in the matter of decision outcomes on the utility of individuals and firms, this will be the first paper to study the adverse effects of quotas on both the quality of the decision made by the judge as well as on the financial outcomes and performance of firms involved in a lawsuit.
\newpage
\section{Analytic Design}
\label{sec:meth}

We have obtained case-level micro data from the ICMS on 4.1 million unique court 
cases between the years 2010 and 2016. The data contains records of all cases that were opened in 2010 for Municipal, Commercial, County and Supreme courts and is much more comprehensive after 2013.  For each case the establishment date, the date when procedures began, resolve and close dates, case type, decision type, party roles and if the case was appealed after and value of claim in the case is reported.

1 million of these cases are matched with ORBIS data, which stores firm level information, using unique a firm ID, allowing us to access firm performance indicators.

Thus far, we show that if a respondent firm is associated with an expeditious decision, then it is also expected to be associated with a worse performance in more tangible indicators such as profit and current assets in the following years of the case closure. (See \ref{fig:figure6} in appendix).

To show the adverse effects in firm performance, we take the following steps.

First of all, using difference in difference estimation, we show that a pre case closure trend for these variables also to be present for Respondents(See \ref{fig:figure4} and \ref{fig:figure5} in appendix). In order to be able to neutralize pre trend effects, we use two approaches.

The first approach adopts Time Aggregation to Difference in Difference Estimation to ignore the time series information.(Bertrand et al., 2003) Using the aggregation method, we create two new variables, "average pre treatment effect" and "average post treatment affect" for firm i as follows:

$$ Performance(Post - Pre)Treatment_i = mean(Performance_{it}) - mean(Performance_{it})$$

where the binary variable $treatment$ reflects the case closure.

\ref{fig:figure6}(see Appendix) shows that for respondents, an average firm performs worse, in terms of profit, in the long term if it has a case that is closed at the end of the month.

The second approach follows Pre Event Trends in the Panel Event Study Design by Freyaldenhoven, Hansen and Shapiro. We locate three time varying instrumental variables, case closure year, case closure month and case closure month day, $\eta_{it}$ that are related with the treatment variable $z_{it}$ and outcome variable $y_{1jt}$ and run the following two stage linear regression.

$$\hat{y_{ijt}} = \hat{\beta_{1j}}*z_{it} + \hat{\beta_{1j}}*\eta_{it} + \epsilon_{it} $$
$$\hat{x_{ijt}} = \hat{\delta_{1j}}*\eta_{it} + \hat{u_{it}} $$
for firm i, firm role j (respondent and plaintiff) and time t.

In \ref{fig:figure7}(see Appendix), we plot the coefficients of the resulting regression. For respondent firms, given with similar pre trends, firms with cases closed at the end of the month perform worse than firms with cases closed at the beginning of the month for more tangible assets.

Finally, we run the difference in difference regression

$$ log(performance_i + 1) = \hat{\beta_1} * treatment_{it} * end_{it} + \hat{\beta_2}*treatment_{it} + \hat{\beta_2} * end_{it} + X_i + \lambda $$

where the binary variable $treatment$ reflects the case closure, $X$ is a vector of court, party roles and category type fixed effects and $\lambda$ is time fixed effects.

In Tables 1 and 2 (see Appendix), we show that in the long run firms with cases closed at the end of the month perform 37\% worse in terms of profit than cases closed in the beginning of the month. The trend is consistent with different combinations of fixed effects.

\section{Work Program}
Daniel Li Chen (Senior Economist, DIME) is the Lead Principal Investigator (PI). Manuel Ramos-Maqueda (Analyst, DIME) is a Principal Investigator in this project. Deniz Tokmakoglu (Research Asistant, DIME) is the research assistant in this project.

In the following steps of the analysis, we are planning to continue

We are planning to conclude our analysis in $xx$ months. Results of the study will be disseminated widely through seminars and peer reviewed publications.

\section{Appendix}
\label{sec:verify}

\subsection{Figure 1 Cases closed by the days of the month}
\begin{figure}[H]
\label{fig:figure1}
    \centering
    \includegraphics[width=8cm]{case_closure_total.jpg}
    \caption{Cases closed by the days of the month}
\end{figure}

\subsection{Figure 2 Percentage of Cases Closed at the End of the Month By Region}
\begin{figure}[H]
  \label{fig:figure2}
    \centering
    \includegraphics[width=8cm]{map_1.jpg}
    \caption{Percentage of Cases Closed at the End of the Month By Region}
\end{figure}
\subsection{Figure 3 Percentage of Appeals by Cases Closed at the End of the Month}
\begin{figure}[H]   
  \label{fig:figure3}
    \centering
    \includegraphics[width=10cm]{Percent_appealed.jpg}
    \caption{There is a discontinuity around the end of the month which signifies that 
    cases closed at the end of the month had more appeals.}
\end{figure}
\subsection{Figure 4 Pre Treatment Effect for Respondent Firms}
\begin{figure}[H]
  \label{fig:figure4}
    \centering
    \includegraphics[width=8cm]{pre_treatment_respondents.jpg}
    \caption{Pre Treatment Effect for Respondent Firms}
\end{figure}
\subsection{Figure 5 Pre - Pre Treatment Effect for Respondent Firms}
\begin{figure}[H]
  \label{fig:figure5}
    \centering
    \includegraphics[width=8cm]{pre_pre_respondent.jpg}
    \caption{Pre - Pre Treatment Effect for Respondent Firms}
\end{figure}
\subsection{Figure 6 Post - Pre Treatment Effect for Respondent Firms}
\begin{figure}[H]
  \label{fig:figure6}
    \centering
    \includegraphics[width=8cm]{plot_respondents_post_pre_profit.jpg}
    \caption{Post - Pre Treatment Effect for Respondent Firms}
\end{figure}
\subsection{Figure 7 Two Stage Linear Regression Coefficients for Respondent Firms}
\begin{figure}[H]
  \label{fig:figure7}
    \centering
    \includegraphics[width=8cm]{respondents_2sls.jpg}
    \caption{Two Stage Linear Regression Coefficients for Respondent Firms}
\end{figure}

\newpage

\begin{landscape}

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{fig:table1} 
\tiny 
\begin{tabular}{@{\extracolsep{2pt}}lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{5}{c}{\textit{Dependent variable:}} \\ 
\cline{2-6} 
\\[-1.8ex] & \multicolumn{5}{c}{log(profit + 1)} \\ 
 & OLS & Court Type Fixed & Category Type Fixed & Party Roles Fixed & Court and Category Types Fixed \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5)\\ 
\hline \\[-1.8ex] 
 After Case Closure & 0.491$^{***}$ & 0.361$^{***}$ & 0.399$^{***}$ & 0.384$^{***}$ & 0.397$^{***}$ \\ 
  & (0.005) & (0.016) & (0.017) & (0.016) & (0.016) \\ 
  Closed at the end of the Month (Days 20, 31) & 0.208$^{***}$ &  &  &  &  \\ 
  & (0.004) &  &  &  &  \\ 
  After Case Closure for cases closed at the end of the month & $-$0.374$^{***}$ & $-$0.368$^{***}$ & $-$0.396$^{***}$ & $-$0.370$^{***}$ & $-$0.395$^{***}$ \\ 
  & (0.006) & (0.022) & (0.022) & (0.021) & (0.022) \\ 
 \hline \\[-1.8ex] 
Observations & 287,505 & 287,505 & 264,417 & 287,505 & 264,417 \\ 
R$^{2}$ & 0.941 & 0.178 & 0.213 & 0.212 & 0.230 \\ 
Adjusted R$^{2}$ & 0.939 & 0.178 & 0.213 & 0.212 & 0.229 \\ 
Residual Std. Error & 0.795 (df = 275632) & 2.907 (df = 287465) & 2.849 (df = 264307) & 2.846 (df = 287440) & 2.819 (df = 264305) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
  \caption{} 
  \label{fig:table2} 
\tiny 
\begin{tabular}{@{\extracolsep{2pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & \multicolumn{3}{c}{log(profit + 1)} \\ 
 & Category Types and Party Roles Fixed & Court Type and Party Roles Fixed & All Fixed \\ 
\\[-1.8ex] & (1) & (2) & (3)\\ 
\hline \\[-1.8ex] 
 After Case Closure & 0.397$^{***}$ & 0.377$^{***}$ & 0.403$^{***}$ \\ 
  & (0.016) & (0.016) & (0.016) \\ 
  Closed at the end of the Month (Days 20, 31) &  &  &  \\ 
  &  &  &  \\ 
  After Case Closure for cases closed at the end of the month & $-$0.392$^{***}$ & $-$0.368$^{***}$ & $-$0.397$^{***}$ \\ 
  & (0.022) & (0.021) & (0.021) \\ 
 \hline \\[-1.8ex] 
Observations & 264,417 & 287,505 & 264,417 \\ 
R$^{2}$ & 0.237 & 0.240 & 0.274 \\ 
Adjusted R$^{2}$ & 0.237 & 0.240 & 0.274 \\ 
Residual Std. Error & 2.805 (df = 264352) & 2.795 (df = 287436) & 2.736 (df = 264278) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\end{landscape}

\begin{tabular}{lll}
\toprule
type & stat & val\\
\midrule
 & Coef & -111569.399\\

 & SE & 26938.086\\

 & t-stat & -4.142\\

\multirow{-4}{*}{\raggedright\arraybackslash Local-Linear} & CI & (-164367.077,-58771.721)\\
\cmidrule{1-3}
 & Coef & -102031.996\\

 & SE & 36941.283\\

 & t-stat & -2.762\\

\multirow{-4}{*}{\raggedright\arraybackslash Robust} & CI & (-174435.581,-29628.412)\\
\cmidrule{1-3}
 & Bandwidth & (14,13)\\

 & Nobs & (14,13)\\

\multirow{-3}{*}{\raggedright\arraybackslash --} & Polynomial Order & 3\\
\bottomrule
\end{tabular}

\section{References}

\begin{referece}
\label{ref:ref1}
de Figueiredo, M., Lahav, A. D., & Siegelman, P. (2017). Do Judges Respond to Incentives? 
The Effects of the Six Month List. SSRN Electronic Journal, 1–74 
\end{referece}

\begin{referece}
Cohen, L., Gurun, U., & Li, D. (2019). Internal Deadlines, Drug Approvals, and Safety Problems. SSRN Electronic Journal, 1–19. https://doi.org/10.2139/ssrn.3427338
\end{referece}

\begin{referece}
Freyaldenhoven, Simon, Christian Hansen, and Jesse M. Shapiro. 2019. "Pre-event Trends in the Panel Event-Study Design." American Economic Review, 109 (9): 3307-38.
\end{referece}

\begin{referece}
Bertrand, M., Duflo, E., &amp; Mullainathan, S. (2002). How much should we trust differences-in-differences estimates? doi:10.3386/w8841
\end{referece}

\begin{referece}
McCrary, J. (2007). Manipulation of the running variable in the regression discontinuity design: A density test. doi:10.3386/t0334
\end{referece}

\begin{referece}
Carpenter, Daniel, and Justin Grimmer. 2009. “The Downside of Deadlines.” Robert
Wood Johnson Scholars in Health Policy Working Paper, 35.
\end{referece}

\begin{referece}
Cohen, L., Gurun, U., & Li, D. (2019). Internal Deadlines, Drug Approvals, and Safety Problems. SSRN Electronic Journal, 1–19. https://doi.org/10.2139/ssrn.3427338
\end{referece}

\begin{referece}
Gregory Lewis and Patrick Bajari, Moral Hazard, Incentive Contracts, and Risk: Evidence from Procurement ,81 REV. ECON. STUD. 1201, 1202 (2014)
\end{referece}

\begin{referece}
Beth Asch, Do Incentives Matter? The Case of Navy Recruiters , 42 IND. LAB. RELAT. REV. 89, 105 (1990)
\end{referece}

\begin{referece}
Paul Oyer, Fiscal Year Ends and Nonlinear Incentive Contracts: The Effect on Business Seasonality , 113 Q. J.ECON. 149-185 (1998)
\end{referece}

\begin{referece}
Michael D. Frakes & Melissa F. Wasserman, Procrastination in the Workplace: Evidence From The U.S. Patent Office (NBER Working Paper 22987, Dec. 2016).
\end{referece}

\begin{referece}
Jeffrey B. Liebman and Neale Mahoney, Do Expiring Budgets Lead to Wasteful Year-End Spending? Evidence from Federal Procurement , 107 AMER. ECON. REV. 3510 (2017)
\end{referece}

\end{document}

### 2021-12-07 paper/main.tex
paper_initialize

@@
 
-The stages for our analysis are as follows. 
-First, we identify that there are more cases closed at the end of the month, which can be considered as an expeditious decision.
-(See \ref{fig:figure1} and \ref{fig:figure2} in appendix), in any given month, for any court type and case type.
-Then we show, that cases closed at the end of the month are more likely to be appealed than cases closed at any other period.
-(See \ref{fig:figure3} in appendix) Subsequently, we examine the performance of firms with different party roles (Respondent and Plaintiff) that are involved with a case in our data using several performance indicators such as firm profit, firm current assets and number of employees in a 6 year time window, 3 years before the closure of the case and 3 years after the closure of the case.
-
-We are hoping to stress the importance of a judicial systems on well being and growth of the county by drawing parallels with the judicial structures and firm performance that derive growth.
-This paper will be the first to evaluate the adverse effects on performance of firms involved in a lawsuit by the quality of the judicial decision.
-The quality of the decision is, in theory, highly affected by the deadlines set by the government.
-
 \section{Literature Review}
 
-Previous research also show the impact of deadline quotas on judge behavior.
-de Figueiredo et al.
-evaluates the effects of a requirement of federal district court judges to publicly release their backlog on their behaviour.
-They report that such a quota incentives judges to close considerably more cases right before the deadline week\href{ref:ref1}{(de Figueiredo et al., 2017)}.
-Similar deadline effects are also present in different fields.
-(Lewis & Bajari, 2014), (Asch, 1990), (Oyer, 1998), (Frakes & Wasserman, 2016) and (Liebman & Mahoney, 2017) discuss the "bunching" of work completion right before the deadline in construction, military recruitment, sales, patent examination and end of the year spending by government agencies respectively.
-Cohen et.al investigates deadlines medical drug approval deadlines.
-Echoed in our research's outline, they first reveal that there is a global surge in drug approvals right before the approval deadlines.
-Consequently, they argue that these swift decisions are associated with more adverse effects such as death, hospitalization etc.
-(Cohen et al., 2019).
-Carpenter and Grimmer discuss the downside of government imposed decision making deadlines and derive a model that demonstrates the increase error rate in decision making.(Daniel & Grimmer., 2009).
-While our research is comparable with de Figueiredo et al.
-in terms of how deadline quotas effect judge behaviour on case closure and Cohen et al.
-in the matter of decision outcomes on the utility of individuals and firms, this will be the first paper to study the adverse effects of quotas on both the quality of the decision made by the judge as well as on the financial outcomes and performance of firms involved in a lawsuit.
-\newpage
-\section{Analytic Design}
-\label{sec:meth}
-
-We have obtained case-level micro data from the ICMS on 4.1 million unique court 
-cases between the years 2010 and 2016.
-The data contains records of all cases that were opened in 2010 for Municipal, Commercial, County and Supreme courts and is much more comprehensive after 2013.
-For each case the establishment date, the date when procedures began, resolve and close dates, case type, decision type, party roles and if the case was appealed after and value of claim in the case is reported.
-
-1 million of these cases are matched with ORBIS data, which stores firm level information, using unique a firm ID, allowing us to access firm performance indicators.
-
-Thus far, we show that if a respondent firm is associated with an expeditious decision, then it is also expected to be associated with a worse performance in more tangible indicators such as profit and current assets in the following years of the case closure.
-(See \ref{fig:figure6} in appendix).
-
-To show the adverse effects in firm performance, we take the following steps.
-
-First of all, using difference in difference estimation, we show that a pre case closure trend for these variables also to be present for Respondents(See \ref{fig:figure4} and \ref{fig:figure5} in appendix).
-In order to be able to neutralize pre trend effects, we use two approaches.
-
-The first approach adopts Time Aggregation to Difference in Difference Estimation to ignore the time series information.(Bertrand et al., 2003) Using the aggregation method, we create two new variables, "average pre treatment effect" and "average post treatment affect" for firm i as follows:
-
-$$ Performance(Post - Pre)Treatment_i = mean(Performance_{it}) - mean(Performance_{it})$$
-
-where the binary variable $treatment$ reflects the case closure.
-
-\ref{fig:figure6}(see Appendix) shows that for respondents, an average firm performs worse, in terms of profit, in the long term if it has a case that is closed at the end of the month.
-
-The second approach follows Pre Event Trends in the Panel Event Study Design by Freyaldenhoven, Hansen and Shapiro.
-We locate three time varying instrumental variables, case closure year, case closure month and case closure month day, $\eta_{it}$ that are related with the treatment variable $z_{it}$ and outcome variable $y_{1jt}$ and run the following two stage linear regression.
-
-$$\hat{y_{ijt}} = \hat{\beta_{1j}}*z_{it} + \hat{\beta_{1j}}*\eta_{it} + \epsilon_{it} $$
-$$\hat{x_{ijt}} = \hat{\delta_{1j}}*\eta_{it} + \hat{u_{it}} $$
-for firm i, firm role j (respondent and plaintiff) and time t.
-
-In \ref{fig:figure7}(see Appendix), we plot the coefficients of the resulting regression.
-For respondent firms, given with similar pre trends, firms with cases closed at the end of the month perform worse than firms with cases closed at the beginning of the month for more tangible assets.
-
-Finally, we run the difference in difference regression
-
-$$ log(performance_i + 1) = \hat{\beta_1} * treatment_{it} * end_{it} + \hat{\beta_2}*treatment_{it} + \hat{\beta_2} * end_{it} + X_i + \lambda $$
-
-where the binary variable $treatment$ reflects the case closure, $X$ is a vector of court, party roles and category type fixed effects and $\lambda$ is time fixed effects.
-
-In Tables 1 and 2 (see Appendix), we show that in the long run firms with cases closed at the end of the month perform 37\% worse in terms of profit than cases closed in the beginning of the month.
-The trend is consistent with different combinations of fixed effects.
-
-\section{Work Program}
-Daniel Li Chen (Senior Economist, DIME) is the Lead Principal Investigator (PI).
-Manuel Ramos-Maqueda (Analyst, DIME) is a Principal Investigator in this project.
-Deniz Tokmakoglu (Research Asistant, DIME) is the research assistant in this project.
-
-In the following steps of the analysis, we are planning to continue
-
-We are planning to conclude our analysis in $xx$ months. Results of the study will be disseminated widely through seminars and peer reviewed publications.
-
-\section{Appendix}
-\label{sec:verify}
-
-\subsection{Figure 1 Cases closed by the days of the month}
-\begin{figure}[H]
-\label{fig:figure1}
-    \centering
-    \includegraphics[width=8cm]{case_closure_total.jpg}
-    \caption{Cases closed by the days of the month}
-\end{figure}
-
-\subsection{Figure 2 Percentage of Cases Closed at the End of the Month By Region}
-\begin{figure}[H]
-  \label{fig:figure2}
-    \centering
-    \includegraphics[width=8cm]{map_1.jpg}
-    \caption{Percentage of Cases Closed at the End of the Month By Region}
-\end{figure}
-\subsection{Figure 3 Percentage of Appeals by Cases Closed at the End of the Month}
-\begin{figure}[H]   
-  \label{fig:figure3}
-    \centering
-    \includegraphics[width=10cm]{Percent_appealed.jpg}
-    \caption{There is a discontinuity around the end of the month which signifies that 
-    cases closed at the end of the month had more appeals.}
-\end{figure}
-\subsection{Figure 4 Pre Treatment Effect for Respondent Firms}
-\begin{figure}[H]
-  \label{fig:figure4}
-    \centering
-    \includegraphics[width=8cm]{pre_treatment_respondents.jpg}
-    \caption{Pre Treatment Effect for Respondent Firms}
-\end{figure}
-\subsection{Figure 5 Pre - Pre Treatment Effect for Respondent Firms}
-\begin{figure}[H]
-  \label{fig:figure5}
-    \centering
-    \includegraphics[width=8cm]{pre_pre_respondent.jpg}
-    \caption{Pre - Pre Treatment Effect for Respondent Firms}
-\end{figure}
-\subsection{Figure 6 Post - Pre Treatment Effect for Respondent Firms}
-\begin{figure}[H]
-  \label{fig:figure6}
-    \centering
-    \includegraphics[width=8cm]{plot_respondents_post_pre_profit.jpg}
-    \caption{Post - Pre Treatment Effect for Respondent Firms}
-\end{figure}
-\subsection{Figure 7 Two Stage Linear Regression Coefficients for Respondent Firms}
-\begin{figure}[H]
-  \label{fig:figure7}
-    \centering
-    \includegraphics[width=8cm]{respondents_2sls.jpg}
-    \caption{Two Stage Linear Regression Coefficients for Respondent Firms}
-\end{figure}
-
-\newpage
-
-\begin{landscape}
-
-\begin{table}[!htbp] \centering 
-  \caption{} 
-  \label{fig:table1} 
-\tiny 
-\begin{tabular}{@{\extracolsep{2pt}}lccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{5}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-6} 
-\\[-1.8ex] & \multicolumn{5}{c}{log(profit + 1)} \\ 
- & OLS & Court Type Fixed & Category Type Fixed & Party Roles Fixed & Court and Category Types Fixed \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5)\\ 
-\hline \\[-1.8ex] 
- After Case Closure & 0.491$^{***}$ & 0.361$^{***}$ & 0.399$^{***}$ & 0.384$^{***}$ & 0.397$^{***}$ \\ 
-  & (0.005) & (0.016) & (0.017) & (0.016) & (0.016) \\ 
-  Closed at the end of the Month (Days 20, 31) & 0.208$^{***}$ &  &  &  &  \\ 
-  & (0.004) &  &  &  &  \\ 
-  After Case Closure for cases closed at the end of the month & $-$0.374$^{***}$ & $-$0.368$^{***}$ & $-$0.396$^{***}$ & $-$0.370$^{***}$ & $-$0.395$^{***}$ \\ 
-  & (0.006) & (0.022) & (0.022) & (0.021) & (0.022) \\ 
- \hline \\[-1.8ex] 
-Observations & 287,505 & 287,505 & 264,417 & 287,505 & 264,417 \\ 
-R$^{2}$ & 0.941 & 0.178 & 0.213 & 0.212 & 0.230 \\ 
-Adjusted R$^{2}$ & 0.939 & 0.178 & 0.213 & 0.212 & 0.229 \\ 
-Residual Std. Error & 0.795 (df = 275632) & 2.907 (df = 287465) & 2.849 (df = 264307) & 2.846 (df = 287440) & 2.819 (df = 264305) \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-  \caption{} 
-  \label{fig:table2} 
-\tiny 
-\begin{tabular}{@{\extracolsep{2pt}}lccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-4} 
-\\[-1.8ex] & \multicolumn{3}{c}{log(profit + 1)} \\ 
- & Category Types and Party Roles Fixed & Court Type and Party Roles Fixed & All Fixed \\ 
-\\[-1.8ex] & (1) & (2) & (3)\\ 
-\hline \\[-1.8ex] 
- After Case Closure & 0.397$^{***}$ & 0.377$^{***}$ & 0.403$^{***}$ \\ 
-  & (0.016) & (0.016) & (0.016) \\ 
-  Closed at the end of the Month (Days 20, 31) &  &  &  \\ 
-  &  &  &  \\ 
-  After Case Closure for cases closed at the end of the month & $-$0.392$^{***}$ & $-$0.368$^{***}$ & $-$0.397$^{***}$ \\ 
-  & (0.022) & (0.021) & (0.021) \\ 
- \hline \\[-1.8ex] 
-Observations & 264,417 & 287,505 & 264,417 \\ 
-R$^{2}$ & 0.237 & 0.240 & 0.274 \\ 
-Adjusted R$^{2}$ & 0.237 & 0.240 & 0.274 \\ 
-Residual Std. Error & 2.805 (df = 264352) & 2.795 (df = 287436) & 2.736 (df = 264278) \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
-
-\end{landscape}
-
-\begin{tabular}{lll}
-\toprule
-type & stat & val\\
-\midrule
- & Coef & -111569.399\\
-
- & SE & 26938.086\\
-
- & t-stat & -4.142\\
-
-\multirow{-4}{*}{\raggedright\arraybackslash Local-Linear} & CI & (-164367.077,-58771.721)\\
-\cmidrule{1-3}
- & Coef & -102031.996\\
-
- & SE & 36941.283\\
-
- & t-stat & -2.762\\
-
-\multirow{-4}{*}{\raggedright\arraybackslash Robust} & CI & (-174435.581,-29628.412)\\
-\cmidrule{1-3}
- & Bandwidth & (14,13)\\
-
- & Nobs & (14,13)\\
-
-\multirow{-3}{*}{\raggedright\arraybackslash --} & Polynomial Order & 3\\
-\bottomrule
-\end{tabular}
-
-\section{References}
-
-\begin{referece}
-\label{ref:ref1}
-de Figueiredo, M., Lahav, A. D., & Siegelman, P. (2017). Do Judges Respond to Incentives? 
-The Effects of the Six Month List. SSRN Electronic Journal, 1–74 
-\end{referece}
-
-\begin{referece}
-Cohen, L., Gurun, U., & Li, D. (2019). Internal Deadlines, Drug Approvals, and Safety Problems. SSRN Electronic Journal, 1–19. https://doi.org/10.2139/ssrn.3427338
-\end{referece}
-
-\begin{referece}
-Freyaldenhoven, Simon, Christian Hansen, and Jesse M. Shapiro. 2019. "Pre-event Trends in the Panel Event-Study Design." American Economic Review, 109 (9): 3307-38.
-\end{referece}
-
-\begin{referece}
-Bertrand, M., Duflo, E., &amp; Mullainathan, S. (2002). How much should we trust differences-in-differences estimates? doi:10.3386/w8841
-\end{referece}
-
-\begin{referece}
-McCrary, J. (2007). Manipulation of the running variable in the regression discontinuity design: A density test. doi:10.3386/t0334
-\end{referece}
-
-\begin{referece}
-Carpenter, Daniel, and Justin Grimmer. 2009. “The Downside of Deadlines.” Robert
-Wood Johnson Scholars in Health Policy Working Paper, 35.
-\end{referece}
-
-\begin{referece}
-Cohen, L., Gurun, U., & Li, D. (2019). Internal Deadlines, Drug Approvals, and Safety Problems. SSRN Electronic Journal, 1–19. https://doi.org/10.2139/ssrn.3427338
-\end{referece}
-
-\begin{referece}
-Gregory Lewis and Patrick Bajari, Moral Hazard, Incentive Contracts, and Risk: Evidence from Procurement ,81 REV. ECON. STUD. 1201, 1202 (2014)
-\end{referece}
-
-\begin{referece}
-Beth Asch, Do Incentives Matter? The Case of Navy Recruiters , 42 IND. LAB. RELAT. REV. 89, 105 (1990)
-\end{referece}
-
-\begin{referece}
-Paul Oyer, Fiscal Year Ends and Nonlinear Incentive Contracts: The Effect on Business Seasonality , 113 Q. J.ECON. 149-185 (1998)
-\end{referece}
-
-\begin{referece}
-Michael D. Frakes & Melissa F. Wasserman, Procrastination in the Workplace: Evidence From The U.S. Patent Office (NBER Working Paper 22987, Dec. 2016).
-\end{referece}
-
-\begin{referece}
-Jeffrey B. Liebman and Neale Mahoney, Do Expiring Budgets Lead to Wasteful Year-End Spending? Evidence from Federal Procurement , 107 AMER. ECON. REV. 3510 (2017)
-\end{referece}
-
 \end{document}

### 2021-12-07 paper/main.tex
paperr

@@
 
-A year ago, Turkey celebrated it's first century of being a democracy and only in 2 years, celebrations for being a republic is on the line.
-Yet, the country, which resides possibly one of the lesser stable regions in the world; suffered a lot during this period, while trying to establish their democratic traditions.
-Having survived 3 coups,
+A year ago, Turkey celebrated a century of being a democracy.
+Now, only 2 years away from the same milestone for being a republic, it is inevitable to think and analyse the trends of Turkish democracy.
+It is reasonable to say, Turkey, which resides possibly one of the lesser stable regions in the world; suffered a lot during this period, while trying to establish their democratic traditions.
+Having survived 3 coups, 3 "soft" coups and numerous economic, political and civil crises, Turkey still maintained regular and somewhat fair elections without interruption, unlike many other countries in a similar political landscape.
+The goal of this paper is to materialise this continuity and uncover the impact of catastrophic events in Turkey to voting behavior and results.
 
-\section{Literature Review}
+\section{Background}
+
+\section{Data and Limitations}
+
+The data is retrieved retrieved from Turkish Statistical Institute, which is the main source for census and election data in Turkey.
+It consists municipal and parliamentary election results.
+Having decided to have a public vote for the president in 2010, Turkey had it's first presidential elections in 2014.
+Since there only has been one more presidential election after, this type of elections are not included in the analysis.
 

### 2021-12-09 preliminary_analysis.Rmd
more data

---
title: "preliminary_regression"
author: "Deniz Tokmakoglu"
date: "12/7/2021"
output: html_document
---

```{r setup, include=FALSE}
library("tidyverse")
library("knitr")
library("stargazer")
library(readstata13)
library(ggplot2)
library("stringr")
library(data.table)
library("reticulate")
library(fixest)
library(sandwich)
library(tidyverse)
library(lubridate)
library(jtools)
library(rdd)
library(ggplot2)
library(WeightIt)
library(DescTools)
library(knitr)
library(extrafont)
library(splines)
library(lubridate)
library(stargazer)
library(dplyr)
library(data.table)
library(janitor)
library(gcookbook)
library(plm)
library(lfe)
library(modelsummary)
library(formattable)
library(lmtest)
```

```{r}
election_all <- read_csv("clean_data/elections_all.csv")
```

# Initial Regression
```{r}
election_all <- election_all %>% 
  mutate(crisis = ifelse(is.na(`crisis type`), 0, 1),
         percent_turnout = ifelse(percent_turnout < 1, 100 * percent_turnout, 
                                  percent_turnout))

reg1 <- lm(percent_turnout ~ crisis, data = election_all)

stargazer(reg1, type = "text")
```

# By Crisis Type

```{r}
reg1 <- lm(percent_turnout ~ `crisis type_civil unrest` + `crisis type_coup` +
             `crisis type_economic` + `crisis type_refugee` + `crisis type_regufee` + 
             `crisis type_soft coup` + `crisis type_terrorism` + `crisis type_war`
, data = election_all)
```

### 2021-12-11 preliminary_analysis.Rmd
not there yer

@@
 library(readstata13)
+
+library("tidyverse")
+library("knitr")
+library("stargazer")
+library(readstata13)
+library(ggplot2)
+library("stringr")
+library(data.table)
+library("reticulate")
+library(fixest)
+library(sandwich)
+library(lmtest)
 library(ggplot2)
@@
 ```{r}
-election_all <- read_csv("clean_data/elections_all.csv")
+election_all <- read_csv("clean_data/all_data_v_event2.csv")
 ```
@@
 ```{r}
+
+election_all <- election_all %>% mutate(event_right_after = ifelse(year_int - event_year <= 4, 1, 0))
+
 election_all <- election_all %>% 
-  mutate(crisis = ifelse(is.na(`crisis type`), 0, 1),
-         percent_turnout = ifelse(percent_turnout < 1, 100 * percent_turnout, 
-                                  percent_turnout))
+  mutate(percent_turnout = ifelse(percent_turnout < 1, 100 * percent_turnout, percent_turnout))
 
-reg1 <- lm(percent_turnout ~ crisis, data = election_all)
+reg1 <- felm(percent_turnout ~ event_right_after, data = election_all)
 
-stargazer(reg1, type = "text")
+reg2 <- felm(percent_turnout ~ event_right_after + kurdish + refugee | city + year , data = election_all)
+
+stargazer(reg1, reg2, type = "text")
 ```
 
-# By Crisis Type
+# Diff and Diff
 
 ```{r}
-reg1 <- lm(percent_turnout ~ `crisis type_civil unrest` + `crisis type_coup` +
-             `crisis type_economic` + `crisis type_refugee` + `crisis type_regufee` + 
-             `crisis type_soft coup` + `crisis type_terrorism` + `crisis type_war`
-, data = election_all)
+election_all2 <- election_all %>% select(city, year_int, election_type,
+                                      percent_turnout, event_year, event)
+
+election_all2 <- election_all2 %>% 
+  mutate(time_to_treat = ifelse(event_year == 0, 0, round((year_int - event_year) / 4)),
+         treat = ifelse(event_year == 0, 0, 1))
+
+election_all2 <- election_all2 %>% filter(time_to_treat <= 10)
+
+mod_twfe = feols(percent_turnout ~ i(time_to_treat, treat, ref = -1) ## Our key interaction: time × treatment status
+		 |city + year_int,                             ## FEs
+		 cluster = ~city ,                          ## Clustered SEs
+		 data = election_all2)
+
+summary(mod_twfe)
+
+iplot(mod_twfe, 
+      xlab = 'Time to treatment',
+      main = 'Event study: Staggered treatment (TWFE)')
 ```

### 2021-12-11 preliminary_analysis.Rmd
coding finished

@@
 library(readstata13)
-
+library(fastDummies)
 library("tidyverse")
@@
 
-# Diff and Diff
+# Event Study
 
@@
 
-summary(mod_twfe)
-
 iplot(mod_twfe, 
@@
 ```
+# Diff and Diff
+
+```{r}
+election_all3 <- election_all2 %>% filter(abs(time_to_treat) <= 3)
+
+election_all3 <- election_all3 %>% mutate(post = ifelse(time_to_treat > 0, 1, 0))
+
+election_all3$treat_post = election_all3$treat * election_all3$post
+
+reg3 <- felm(percent_turnout ~ treat_post | city + year_int, data = election_all3)
+stargazer(reg3, type = 'text')
+```
+# Swing
+
+```{r}
+election_all4 <- election_all %>%select(city, year_int, election_type,
+                                      percent_turnout, event_year, event, swing,
+                                      incumbent_vote_share, prev_winner_voteshare)
+
+election_all4 <- election_all4 %>% 
+  mutate(time_to_treat = ifelse(event_year == 0, 0, 
+                                round((year_int - event_year) / 4)),
+         treat = ifelse(event_year == 0, 0, 1))
+
+election_all4 <- election_all4 %>% mutate(post = 
+                                            ifelse(time_to_treat > 0, 1, 0))
+
+election_all4 <- election_all4 %>% filter(abs(time_to_treat) <= 3)
+
+election_all4$treat_post = election_all4$treat * election_all4$post
+
+reg4 <- felm(swing ~ treat_post | city + year_int, 
+             data = election_all4)
+stargazer(reg4, type = 'text')
+```
+
+# Non Swing Vote Share
+```{r}
+
+election_all5 <- election_all4 %>% filter(swing == 0)
+
+election_all5$change_vote = election_all5$incumbent_vote_share - 
+  election_all5$prev_winner_voteshare
+
+election_all5$id = paste(election_all5$city, election_all5$year_int, election_all5$election_type)
+
+reg5 <- felm(incumbent_vote_share ~ treat_post | city + year_int , 
+             data = election_all5)
+
+reg6 <- felm(change_vote ~ treat_post | city + year_int, 
+             data = election_all5)
+
+stargazer(reg5, reg6, type = 'text')
+```
+
+#Swing Vote Share
+
+```{r}
+election_all6 <- election_all4 %>% filter(swing == 1)
+
+election_all6$change_vote = election_all6$incumbent_vote_share - 
+  election_all6$prev_winner_voteshare
+
+reg7 <- felm(change_vote ~ treat_post | city + year_int, 
+             data = election_all6)
+stargazer(reg7, type = 'text')
+```
+
+# Event Spesific
+
+```{r}
+dummies <- dummy_cols(election_all4, select_columns = 'event', ignore_na = TRUE)
+
+dummies <- dummies %>% mutate(event_earthquake = replace_na(event_earthquake, 0),
+                              `event_kurdish war` = replace_na(`event_kurdish war`, 0),
+                              `event_cyprus war` = replace_na(`event_cyprus war`, 0),
+                              event_refugee = replace_na(`event_refugee`, 0))
+
+dummies$treat_post_kurdish = dummies$`event_kurdish war` * dummies$post
+dummies$event_earthquake = dummies$event_earthquake * dummies$post
+dummies$treat_post_cyprus = dummies$`event_cyprus war` * dummies$post
+dummies$treat_post_refugee = dummies$event_refugee * dummies$post
+
+dummies$change_vote = dummies$incumbent_vote_share - dummies$prev_winner_voteshare
+
+reg1_1 <- felm(incumbent_vote_share ~ treat_post_kurdish | city + year_int, 
+             data = dummies)
+reg1_2 <- felm(incumbent_vote_share ~ event_earthquake | city + year_int, 
+             data = dummies)
+reg1_3 <- felm(incumbent_vote_share ~ treat_post_cyprus | city + year_int, 
+             data = dummies)
+reg1_4 <- felm(incumbent_vote_share ~ treat_post_refugee | city + year_int, 
+             data = dummies)
+
+stargazer(reg1_1, reg1_2, reg1_3, reg1_4, type = 'text')
+
+reg2_1 <- felm(change_vote ~ treat_post_kurdish | city + year_int, 
+             data = dummies)
+reg2_2 <- felm(change_vote ~ event_earthquake | city + year_int, 
+             data = dummies)
+reg2_3 <- felm(change_vote ~ treat_post_cyprus | city + year_int, 
+             data = dummies)
+reg2_4 <- felm(change_vote ~ treat_post_refugee | city + year_int, 
+             data = dummies)
+
+stargazer(reg2_1, reg2_2, reg2_3, reg2_4, type = 'text')
+
+reg3_1 <- felm(swing ~ treat_post_kurdish | city + year_int, 
+             data = dummies)
+reg3_2 <- felm(swing ~ event_earthquake | city + year_int, 
+             data = dummies)
+reg3_3 <- felm(swing ~ treat_post_cyprus | city + year_int, 
+             data = dummies)
+reg3_4 <- felm(swing ~ treat_post_refugee | city + year_int, 
+             data = dummies)
+
+stargazer(reg3_1, reg3_2, reg3_3, reg3_4, type = 'text')
+
+dummies_swing <- dummies %>% filter(swing == 1)
+
+reg4_1 <- felm(incumbent_vote_share ~ treat_post_kurdish | city + year_int, 
+             data = dummies_swing)
+reg4_2 <- felm(incumbent_vote_share ~ event_earthquake | city + year_int, 
+             data = dummies_swing)
+reg4_3 <- felm(incumbent_vote_share ~ treat_post_cyprus | city + year_int, 
+             data = dummies_swing)
+reg4_4 <- felm(incumbent_vote_share ~ treat_post_refugee | city + year_int, 
+             data = dummies_swing)
+
+stargazer(reg4_1, reg4_2, reg4_3, reg4_4, type = 'text')
+```

### 2021-12-11 paper/main.tex

@@
 
+\subsection{Brief Summary of Turkish History}
+
+After the end of World War I, like many empires in Europe; Ottoman Empire crumbled.
+In it's heartland, Turkey emerged as a new republic in 1923 after a long period of successive independence war against the colonial powers.
+
+Founded as a parliamentary republic, the first 17 years of the country has been defined by a single party period in which the founding party Republican People's Party, (Turkish abbreviation CHP will be used thereafter) was in power.
+The party is defined by having pro-European, Liberal and Secular values.
+Only in 1950, Turkey had it's truly first election with emergence of Right wing parties.
+Between 1950 - 2018, Turkey remained as a parliamentary republic with periodic municipal and parliamentary elections.
+
+In 2018, with a 51\% referendum result, Turkey decided to transition into a presidential republic where the president and the Parliament is elected at the same time, using different ballots.
+For this project's scope Turkey's only 2 presidential elections were excluded from research.
+
+Inheriting many problems of it's predecessor, since it's foundation Turkey needed to deal with both regional and domestic problems.
+Composed of many different ethnic backgrounds such as Turkish, Kurdish, Armenian, Zaza etc.
+Turkey had to actively fight to maintain it's regional integrity.
+Moreover, as the gateway of Middle East to Europe, Turkey suffered from many regional events taking place outside of it's borders.
+One great example of this is the refugee influx to Turkey after ISIS war in Syria in 2011.
+
+\subsection{Summary of Catastrophic Events}
+
+The research consists of 4 main catastrophic events, which will be used to analyze voter behaviour.
+
+\subsubsection{1999 Marmara Earthquake}
+
+On August 17, 1999 the Marmara Region in Turkey was devastated from
+
 \section{Data and Limitations}

### 2021-12-11 paper/main.tex
paper_changes

@@
 \usepackage{hyperref}
+\usepackage{appendixnumberbeamer}
+\usepackage{multicol}
+\usepackage{booktabs}
+\usepackage{outlines} % new package, delete if getting package errors
+\usepackage[scale=2]{ccicons}
+\usepackage{graphicx}
+\usepackage{pgfplots}
+\usepgfplotslibrary{dateplot}
+\usepackage{subcaption}
+\captionsetup{compatibility=false}
+\usepackage{xspace}
+\usepackage{tikz}
+\usepackage{newtxtext}
 \usepackage{titlesec}
@@
 \subsubsection{1999 Marmara Earthquake}
+On August 17, 1999 the Marmara Region in Turkey was devastated from a 7.5 magnitude earthquake that lasted for several days.
+Most of the buildings in the epicenter of the earthquake were either severely damaged or collapsed by the end of the event.
+Approximately 18,000 people were killed.
+It was a showcase of Turkey's unpreparedness for earthquakes, a country which sits on various earthquake lines.
 
-On August 17, 1999 the Marmara Region in Turkey was devastated from
+\begin{subfigure}[t]{.49\textwidth}
+    \includegraphics[scale=0.15]{paper/figures/earthquake_marmara2.jpeg}
+	\caption{Marmara Earthquake}
+	\end{subfigure}
+	\begin{subfigure}[t]{.49\textwidth}
+    \includegraphics[scale=0.3]{paper/figures/marmara_affected.jpeg}
+	\caption{Regions Affected}
+\end{subfigure}
+
+\subsubsection{1974 Cyprus Peace Operation}
+
+The island of Cyprus, which used to be ruled entirely by Republic of Cyprus lies in the Eastern Mediterranean, approximately 70km away from the Turkish mainland.
+The island is composed of Cypriot Greeks and Cypriot Turks.
+While the latter is the minority, the founding principles of the Republic of Cyprus ensured equal representation for both, and assigned Turkey, Greece and the UK as guarantor states.
+All had the ability to intervene if the ethnic groups they represent were in danger.
+The tension in the island was ever increasing with Turkish minority under attack by Greek Nationalist organizations but the tipping point was in 1974; when a pro Greek unification president got elected in the island.
+
+Turkey decided to intervene, causing relocation of many Greek and Turkish locals and separation of the island into 2.
+The north declared it's independence as Turkish Republic of Northern Cyprus; which is only recognized by Turkey.
+
+\subsubsection{2011 Refugee Crisis}
+
+In 2011, a civil war started in Syria after a set of peaceful student demonstrations caused the government's crackdown.
+80\% of the Syrians got displaced and the majority of them entered to Turkey via the border, making Turkey the largest refugee holder in the world since 2014.
+
+\subsubsection{1984 Conflict with Kurdish Armed Groups}
+
+Composing one fifth of Turkey's population, ethnic Kurdish people mostly live in the Eastern cities in Turkey (mainly Van, Diyarbakir).
+The PKK (Kurdish Worker's Party), established by Abdullah Ocalan in 1978, has waged an insurgency since 1984 against Turkish authorities for greater cultural and political rights, primarily with the objective of establishing an independent Kurdish state.
+The ongoing conflict in the eastern region has resulted in nearly forty thousand deaths.
+The organization has been labelled as a terrorist organization by Turkey and it's allies.
 
@@
 It consists municipal and parliamentary election results.
-Having decided to have a public vote for the president in 2010, Turkey had it's first presidential elections in 2014.
-Since there only has been one more presidential election after, this type of elections are not included in the analysis.
+It consists of the election year, city, election type, percentage turnout, winning party and the vote share, previous winning party and vote share.
+
+The process of data cleaning and creation can be found in
+
+--
+
+\section{Research Design}
+
+\section{Results}
+
+\section{Conclusion}
 

### 2021-12-11 preliminary_analysis.Rmd
change in regressions

@@
 reg3 <- felm(percent_turnout ~ treat_post | city + year_int, data = election_all3)
-stargazer(reg3, type = 'text')
+stargazer(reg3, type = 'text',
+          title = c("Effects of a Catastrophic Event on Voter Turnout"),
+          column.labels = c('Voter Turnout'),
+          covariate.labels = c('Treatment Effect'),
+          dep.var.labels = c(''))
 ```
@@
 
-reg5 <- felm(incumbent_vote_share ~ treat_post | city + year_int , 
-             data = election_all5)
-
-reg6 <- felm(change_vote ~ treat_post | city + year_int, 
+reg5 <- felm(incumbent_vote_share ~ treat_post | city + year_int + election_type , 
              data = election_all5)
@@
 stargazer(reg4_1, reg4_2, reg4_3, reg4_4, type = 'text')
+
+reg5_1 <- felm(percent_turnout ~ treat_post_kurdish | city + year_int, 
+             data = dummies)
+reg5_2 <- felm(percent_turnout ~ event_earthquake | city + year_int, 
+             data = dummies)
+reg5_3 <- felm(percent_turnout ~ treat_post_cyprus | city + year_int, 
+             data = dummies)
+reg5_4 <- felm(percent_turnout ~ treat_post_refugee | city + year_int, 
+             data = dummies)
+
+stargazer(reg5_1, reg5_2, reg5_3, reg5_4, type = 'text')
 ```

### 2021-12-11 paper/main.tex
Updates from Overleaf

@@
 \usepackage{indentfirst}
+\usepackage{caption}
 \usepackage{hyperref}
@@
 
-\section{Results}
+The main research goal of this paper is to uncover effects of regional crises on voter behavior. To define voter behaviour, percentage turnout and the vote share of the winning party is used.
+
+The research follows Difference in Difference design where each city got affected by an event is compared wit itself (pre-event and post-event) and other cities in the country that has not been effected by an event.
+The regression format is as follows;
+
+$$ Y_i = \beta_{1} + {event * post\_event} + \beta_{2} * {event} + \beta_{3} * {post\_event} + \theta_i$$
+
+Where $Y_i$ is the outcome of interest and $\theta_i$ is year, city and election type fixed effects.
+
+To make the catastrophic event more relevant with election results, only the preceding 2 and suceeding 2 elections were considered in the analysis.
+
+The research is conducted in three levels:
+
+\subsection{Voter Turnout}
+
+On this level, the outcome of interest is Voter Turnout and the regression is conducted for the entire sample.
+This is to understand whether catastrophic events change voter confidence in democracy or make elections a matter of 'life and death'.
+
+\subsection{Outcome}
+
+For this level, 2 outcome of interests are present.
+First, whether to see if the city punishes the ruling party after a catastrophic event.
+This can be tracked by comparing the winner of the election with the previous winner to see if there is a swing.
+
+The second outcome of interest is the level of incumbent vote for cities that did not change the ruling party after an event.
+This is to understand how much the voter values the government's response to a catastrophic event which is explained by the difference in the vote share of the continuing ruling party.
+
+\subsection{Heterogeneous Event Effects}
+
+The third level of the analysis is to uncover the specific effects of each (type) of event on vote outcome and voter turnout.
+This is potentially to understand what type of events speak to the Turkish voters and uncover regional differences in response to the same type of events.
+
+\section{Results and Discussion}
+
+\subsection{Voter Turnout}
+
+As results indicate on Table A1, an event does not change voter tendency to vote.
+This can indicate that Turkish belief in democratic institutions does not change with a catastrophic event.
+This is to be expected as traditionally, Turkish turnout in voting is always one of the highest in the world.
+
+\subsection{Vote Outcome}
+
+From table A2, it appears that the vote share of the same ruling party increases by 6\% after a catastrophic event.
+This means cities that experienced a catastrophic event puts event more faith into the ruling party.
+This can also potentially be explained by the 'rallying' effect of wars.
+Yet, this result is also expected as Turkish voters historically lost faith in the ruling party only after economic crises, which is not included in the scope of this research.
+
+Arguably, Table A3 suggests that cities do not swing after a catastrophic event, which means the voter is not punishing the incumbent party for the event.
+
+\subsection{Heterogeneous Event Effects}
 
@@
 
+\section{Appendix}
+\captionsetup[table]{name=Table A}
+\begin{table}[!htbp] \centering 
+  \caption{Effects of a Catastrophic Event on Voter Turnout} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-2} 
+\\[-1.8ex] &  \\ 
+ & Voter Turnout \\ 
+\hline \\[-1.8ex] 
+ Treatment Effect & 0.640 \\ 
+  & (0.650) \\ 
+  & \\ 
+\hline \\[-1.8ex] 
+Observations & 200 \\ 
+R$^{2}$ & 0.894 \\ 
+Adjusted R$^{2}$ & 0.855 \\ 
+Residual Std. Error & 2.697 (df = 146) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+\begin{table}[!htbp] \centering 
+  \caption{Effects of a Catastrophic Event on Incumbent Vote Share} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-2} 
+\\[-1.8ex] &  \\ 
+ & Incumbent Vote Share \\ 
+\hline \\[-1.8ex] 
+ Treatment Effect & 6.310$^{***}$ \\ 
+  & (2.133) \\ 
+  & \\ 
+\hline \\[-1.8ex] 
+Observations & 117 \\ 
+R$^{2}$ & 0.863 \\ 
+Adjusted R$^{2}$ & 0.759 \\ 
+Residual Std. Error & 5.848 (df = 66) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+ & \multicolumn{1}{r}{Only elections with non-swing result are considered.} \\ 
+\end{tabular} 
+\end{table}
+
+\begin{table}[!htbp] \centering 
+  \caption{Effects of a Catastrophic Event on Change in Leadership} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-2} 
+\\[-1.8ex] &  \\ 
+ & Dummy for Leadership Change \\ 
+\hline \\[-1.8ex] 
+ Treatment Effect & $-$0.040 \\ 
+  & (0.080) \\ 
+  & \\ 
+\hline \\[-1.8ex] 
+Observations & 200 \\ 
+R$^{2}$ & 0.668 \\ 
+Adjusted R$^{2}$ & 0.548 \\ 
+Residual Std. Error & 0.332 (df = 146) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
 \end{document}

### 2021-12-11 preliminary_analysis.Rmd
graphics

@@
 
-reg3 <- felm(percent_turnout ~ treat_post | city + year_int, data = election_all3)
-stargazer(reg3, type = 'text',
+reg3 <- felm(percent_turnout ~ treat_post | city + year_int + election_type, data = election_all3)
+stargazer(reg3, type = 'latex',
           title = c("Effects of a Catastrophic Event on Voter Turnout"),
@@
 
-reg4 <- felm(swing ~ treat_post | city + year_int, 
+reg4 <- felm(swing ~ treat_post | city + year_int + election_type, 
              data = election_all4)
-stargazer(reg4, type = 'text')
+stargazer(reg4, type = 'latex',
+          title = c("Effects of a Catastrophic Event on Change in Leadership"),
+          column.labels = c('Dummy for Leadership Change'),
+          covariate.labels = c('Treatment Effect'),
+          dep.var.labels = c('')
+          )
 ```
@@
 
-stargazer(reg5, reg6, type = 'text')
+stargazer(reg5, type = 'latex',
+          title = c("Effects of a Catastrophic Event on Incumbent Vote Share"),
+          column.labels = c('Incumbent Vote Share'),
+          covariate.labels = c('Treatment Effect'),
+          dep.var.labels = c(''),
+          notes = c('Only elections with non-swing result are considered.'))
 ```
@@
 
-reg1_1 <- felm(incumbent_vote_share ~ treat_post_kurdish | city + year_int, 
+reg1_1 <- felm(incumbent_vote_share ~ treat_post_kurdish | city + year_int + election_type, 
              data = dummies)
-reg1_2 <- felm(incumbent_vote_share ~ event_earthquake | city + year_int, 
+reg1_2 <- felm(incumbent_vote_share ~ event_earthquake | city + year_int+ election_type, 
              data = dummies)
-reg1_3 <- felm(incumbent_vote_share ~ treat_post_cyprus | city + year_int, 
+reg1_3 <- felm(incumbent_vote_share ~ treat_post_cyprus | city + year_int+ election_type, 
              data = dummies)
-reg1_4 <- felm(incumbent_vote_share ~ treat_post_refugee | city + year_int, 
+reg1_4 <- felm(incumbent_vote_share ~ treat_post_refugee | city + year_int+ election_type, 
              data = dummies)
 
-stargazer(reg1_1, reg1_2, reg1_3, reg1_4, type = 'text')
+stargazer(reg1_1, reg1_2, reg1_3, reg1_4, type = 'latex',
+          title = c("Effects of a Catastrophic Event on Incumbent Vote Share"),
+          dep.var.labels = c('Incumbent Vote Share'),
+          covariate.labels = c('Kurdish Armed Conflict', 'Marmara Earthquake',
+                               'Cyprus Peace Operation', 'Syrian Refugees'),
+          notes = c('Only elections with non-swing result are considered.'))
 
@@
 
-stargazer(reg5_1, reg5_2, reg5_3, reg5_4, type = 'text')
+stargazer(reg5_1, reg5_2, reg5_3, reg5_4, type = 'latex',
+           title = c("Effects of a Catastrophic Event on Voter Turnout"),
+           dep.var.labels = c('Voter Turnout'),
+           covariate.labels = c('Kurdish Armed Conflict', 'Marmara Earthquake',
+                                 'Cyprus Peace Operation', 'Syrian Refugees'),
+            notes = c('Only elections with non-swing result are considered.'))
 ```

### 2021-12-11 paper/main.tex
Updates from Overleaf

@@
 \usepackage{float}
+\usepackage{blindtext}
+\usepackage{hyperref}
 \usepackage{booktabs,dcolumn}
@@
 
+\doublespacing
 \begin{document}
@@
 
-\section{Data and Limitations}
+\section{Data and Summary Statistics}
 
 The data is retrieved retrieved from Turkish Statistical Institute, which is the main source for census and election data in Turkey.
-It consists municipal and parliamentary election results.
-It consists of the election year, city, election type, percentage turnout, winning party and the vote share, previous winning party and vote share.
+It consists 139 municipal and 264 parliamentary election results on a city and year level.
+The main columns of interest are the election year, city, election type, percentage turnout, winning party and the vote share, previous winning party and vote share.
 
-The process of data cleaning and creation can be found in
-
---
+The process of data cleaning and creation can be found in the author's \href{https://github.com/deniztokmakoglu/turkish_election_analysis}{github page.}
 
@@
 
-\section{Conclusion}
+The 'rallying' effect' is clearly visible under table A4 as the vote share of the incumbent is increased by 17 and 15 percent respectively after Kurdish Armed Conflict and Cyprus Peace Operation events.
+One thing to note though, the regions effected by Kurdish Armed Conflict are traditionally ruled by parties that also have Kurdish identities.
+Therefore, the change in vote share might be explained as political efforts to legitimize Kurdish presence.
+This however, does not imply that the military operations and parties with Kurdish tendencies have anything to do with one another.
 
+Conversely, according to table A5, voter turnout in cities affected by the Kurdish Armed Conflict was 4 percent less than other cities.
+One possible explanation is that after armed conflict; some supporters of increased autonomy for Kurdish people might have lost faith in the democratic means of representation.
+Another possible explanation is the same people might have lost confidence in the cause as they would have thought armed conflict is not the way to gain further rights.
+
+Finally, Syrian Refugee crisis increased the voter turnout by 3 percent in the affected cities. 
+\newpage
 \section{Appendix}
@@
 \end{table} 
+\begin{table}[!htbp] \centering 
+  \caption{Effects of a Catastrophic Event on Incumbent Vote Share} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{4}{c}{Incumbent Vote Share} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
+\hline \\[-1.8ex] 
+ Kurdish Armed Conflict & 28.609$^{***}$ &  &  &  \\ 
+  & (7.097) &  &  &  \\ 
+  & & & & \\ 
+ Marmara Earthquake &  & 5.044 &  &  \\ 
+  &  & (4.238) &  &  \\ 
+  & & & & \\ 
+ Cyprus Peace Operation &  &  & 20.260$^{***}$ &  \\ 
+  &  &  & (5.659) &  \\ 
+  & & & & \\ 
+ Syrian Refugees &  &  &  & $-$1.129 \\ 
+  &  &  &  & (5.580) \\ 
+  & & & & \\ 
+\hline \\[-1.8ex] 
+Observations & 117 & 117 & 117 & 117 \\ 
+R$^{2}$ & 0.875 & 0.848 & 0.870 & 0.845 \\ 
+Adjusted R$^{2}$ & 0.781 & 0.733 & 0.771 & 0.727 \\ 
+Residual Std. Error (df = 66) & 5.575 & 6.158 & 5.695 & 6.221 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+ & \multicolumn{4}{r}{Only elections with non-swing result are considered.} \\ 
+\end{tabular} 
+\end{table}
+
+\begin{table}[!htbp] \centering 
+  \caption{Effects of a Catastrophic Event on Voter Turnout} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{4}{c}{Voter Turnout} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
+\hline \\[-1.8ex] 
+ Kurdish Armed Conflict & $-$4.329$^{**}$ &  &  &  \\ 
+  & (1.905) &  &  &  \\ 
+  & & & & \\ 
+ Marmara Earthquake &  & 1.247 &  &  \\ 
+  &  & (1.144) &  &  \\ 
+  & & & & \\ 
+ Cyprus Peace Operation &  &  & 1.450 &  \\ 
+  &  &  & (1.723) &  \\ 
+  & & & & \\ 
+ Syrian Refugees &  &  &  & 2.266 \\ 
+  &  &  &  & (1.772) \\ 
+  & & & & \\ 
+\hline \\[-1.8ex] 
+Observations & 200 & 200 & 200 & 200 \\ 
+R$^{2}$ & 0.893 & 0.890 & 0.890 & 0.890 \\ 
+Adjusted R$^{2}$ & 0.855 & 0.851 & 0.850 & 0.851 \\ 
+Residual Std. Error (df = 147) & 2.698 & 2.734 & 2.739 & 2.730 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+\begin{table}[!htbp] \centering 
+  \caption{Effects of a Catastrophic Event on Voter Turnout} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{4}{c}{Voter Turnout} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
+\hline \\[-1.8ex] 
+ Kurdish Armed Conflict & $-$4.180$^{**}$ &  &  &  \\ 
+  & (1.881) &  &  &  \\ 
+  & & & & \\ 
+ Marmara Earthquake &  & 1.398 &  &  \\ 
+  &  & (1.128) &  &  \\ 
+  & & & & \\ 
+ Cyprus Peace Operation &  &  & 1.588 &  \\ 
+  &  &  & (1.699) &  \\ 
+  & & & & \\ 
+ Syrian Refugees &  &  &  & 3.282$^{*}$ \\ 
+  &  &  &  & (1.778) \\ 
+  & & & & \\ 
+\hline \\[-1.8ex] 
+Observations & 200 & 200 & 200 & 200 \\ 
+R$^{2}$ & 0.896 & 0.894 & 0.893 & 0.895 \\ 
+Adjusted R$^{2}$ & 0.859 & 0.855 & 0.855 & 0.857 \\ 
+Residual Std. Error (df = 146) & 2.662 & 2.692 & 2.698 & 2.675 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
 

### 2021-12-11 paper/main.tex
Updates from Overleaf
new figures

@@
 }
+\author{\name Deniz Tokmakoglu\\
+       \addr Harris Public Policy and Department of Computer Science\\
+       \address{\href{https://github.com/deniztokmakoglu/turkish_election_analysis}{GitHub}}}
+\maketitle
 
@@
 
-The process of data cleaning and creation can be found in the author's \href{https://github.com/deniztokmakoglu/turkish_election_analysis}{github page.}
+Turkish election turnout is higher than most of the other democracies in the world.
+For all the election types and regions, the average turnout is $84\%$ Cities with the highest turnout appear to be on the east and south regions of Turkey, Istanbul being the exception.
+
+\begin{figure}[h]
+ \centering
+\includegraphics[width=15cm]{paper/turnout_selected.png}
+ \caption{Average Turnout for Selected Cities}
+\end{figure}
+\newpage
+Cities in the South and East also appear to be shifting incumbent parties more than other cities, again Istanbul being an exception.
+While Eastern cities (Diyarbakır, Mardin and Van) always choose incumbent parties with same characteristics, cities like Adana always shift between Right and Left wing parties.
+
+\begin{figure}[h]
+ \centering
+\includegraphics[width=15cm]{paper/change_party.png}
+ \caption{Average Turnout for Selected Cities}
+\end{figure}
 

### 2021-12-12 paper/main.tex

@@
 }
-\author{\name Deniz Tokmakoglu\\
-       \addr Harris Public Policy and Department of Computer Science\\
-       \address{\href{https://github.com/deniztokmakoglu/turkish_election_analysis}{GitHub}}}
+\author{\name Deniz Tokmako{\u{g}}lu\\
+       \addr University of Chicago\\Harris Public Policy and Department of Computer Science\\
+       \address{\href{https://github.com/deniztokmakoglu/turkish_election_analysis}{GitHub Page}}}
 \maketitle
@@
 
+Finally, the emergence of right wing parties and Political Islam is clearly observable in Turkish Election results. Given is the party tendencies of Municipal Election winners over the years.
+
+\begin{figure}[h]
+ \centering
+\includegraphics[width=15cm]{paper/ideologies.png}
+ \caption{Average Turnout for Selected Cities}
+\end{figure}
+\newpage
+
+It is also obvious that this emergence occurred in the expense of left wing parties. However 2019 elections suggest that the trend started to reverse.
+
 \section{Research Design}
@@
 Finally, Syrian Refugee crisis increased the voter turnout by 3 percent in the affected cities.
+
+\section{Conclusion}
+
+The purpose of this research was to understand the impact of regional catastrophic events on Turkish voter behaviour.
+While it is obvious that turnout and incumbent parties do not change right after the event, some events (especially armed conflict or war) increases the trust in the current ruling party.
+While this does not establish causality; the results of this paper suggest that there definitely is a relation between the two.
+
+\section{References}
+Council on Foreign Relations.
+(n.d.).
+Conflict between Turkey and armed Kurdish groups | global conflict tracker.
+Council on Foreign Relations.
+Retrieved December 12, 2021, from https://www.cfr.org/global-conflict-tracker/conflict/conflict-between-turkey-and-armed-kurdish-groups.
+
+Weissmann, A., &amp; Special to The Washington Post; Arnie Weissmann is a freelance writer who recently spent three months on Cyprus.
+(1984, January 22).
+Cyprus sights: Both sides now.
+The Washington Post.
+Retrieved December 12, 2021, from \\https://www.washingtonpost.com/archive/lifestyle/travel/1984/01/22/cyprus-sights-both-sides-now/413143fc-9424-40d5-b894-d1a6c64c332d/.
+
+Platform, I.
+R.
+(n.d.).
+Marmara earthquake, 1999 - countries &amp; disasters.
+International Recovery Platform.
+Retrieved December 12, 2021, from \\https://www.recoveryplatform.org/countries\_and\_disasters/disaster/26/marmara\_earthquake\_1999.
+
+Reid, K.
+(2021, July 13).
+Syrian refugee crisis: Facts, faqs, and how to help.
+World Vision.
+Retrieved December 12, 2021, from\\ https://www.worldvision.org/refugees-news-stories/syrian-refugee-crisis-facts.
+
+Turkish Statistical Institue.
+(n.d.).
+Parlimentary and Municipality Election Database.
+Turkish Statistical Institute Database for Election and Justice.
+Retrieved December 12, 2021, from https://data.tuik.gov.tr/Kategori/GetKategori?p=adalet-ve-secim-110&amp;dil=2.
+
 \newpage
+
 \section{Appendix}

### 2021-12-12 paper/main.tex
Updates from Overleaf

@@
 
-\begin{subfigure}[t]{.49\textwidth}
-    \includegraphics[scale=0.15]{paper/figures/earthquake_marmara2.jpeg}
-	\caption{Marmara Earthquake}
-	\end{subfigure}
-	\begin{subfigure}[t]{.49\textwidth}
-    \includegraphics[scale=0.3]{paper/figures/marmara_affected.jpeg}
-	\caption{Regions Affected}
-\end{subfigure}
+\begin{figure}[h]%
+    \centering
+    \subfloat[\centering Scene from Marmara Earthquake ]{{\includegraphics[width=7.1cm]{paper/figures/earthquake_marmara2.jpeg} }}%
+    \qquad
+    \subfloat[\centering Regions Affected]{{\includegraphics[width=7.1cm]{paper/figures/marmara_affected.jpeg} }}%
+    \caption{Marmara Earthquake}%
+    \label{fig:example}%
+\end{figure}
 
